formula1

### 2020-05-26 inst/skating_analysis.Rmd
fixes #56

```{r,convertordertosupport}
head(ordertable2supp(skating_table))
```

@@

```{r}
jj <-
    matrix(c(
        -1, 0, 0,   1,0,  # Hughes   < Cohen
         0,-1, 0,   1,0,  # Slutskya < Cohen
         0, 0,-1,   1,0,  # Kwan     < Cohen

@@

```{r}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
class(o) <- "matrix"
o
o <- o[,1:7]
o
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
class(o) <- "ranktable"
o
o <- ranktable_to_ordertable(o)
o
o <- ordertable2supp(o)
o
o <- maxp(o)
pie(o)
```

>>>>

```{r,convertordertosupport}
head(ordertable2supp(skating_table,misslast=FALSE))
```

@@

```{r,longthing,cache=TRUE}
jj <-
    matrix(c(
        -1, 0, 0,   1,0,  # Hughes   < Cohen
         0,-1, 0,   1,0,  # Slutskya < Cohen
         0, 0,-1,   1,0,  # Kwan     < Cohen

@@

```{r}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
```

```{r}
class(o) <- "matrix"
o
```

Select just the top seven:
```{r}
o <- o[,1:7]
o
```

and now replace ranks with internal ranks (that is, rank among the top seven):

```{r}
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
```

Now coece to a `ranktable`:

```{r}
class(o) <- "ranktable"
o
```

Thence to an order table:

```{r}
o <- ranktable_to_ordertable(o)
o
```

Now create a likelihood function:

```{r}
o <- ordertable2supp(o,misslast=FALSE)
o
```
and have some fun with it:

```{r}
o <- maxp(o)
pie(o)
```
